\section{How to build Inviwo with ENVISIoN on Ubuntu
18.04 LTS}

\label{ch:install}
These instructions show how to build Inviwo and ENVISIoN on Ubuntu
18.04 LTS.

\subsection{Install git}
Start by installing git, which will be used to fetch ENVISIoN in the
next step.
\begin{lstlisting}[frame = single, breaklines=true]
    sudo apt install git
\end{lstlisting}

\subsection{Download ENVISIoN}
Go to your home folder and clone ENVISIoN from Github. This guide will
assume that both ENVISIoN and Inviwo will be placed directly under the
home folder.
\begin{lstlisting}[frame = single, breaklines=true]
    cd
    git clone https://github.com/rartino/ENVISIoN
\end{lstlisting}

\subsection{Prepare Inviwo using the ENVISIoN install script}
ENVISIoN provides an install script for Ubuntu 18.04 LTS. Executing
the installation script will install all required dependencies, clone
Inviwo from Github and configure the Inviwo build.

The script should \emph{NOT} be run as root, but as your own user and
it will ask for your password when it needs root rights. It is
possible that the script will ask for other user input during the
process, if that's the case, just accept the default.
\begin{lstlisting}[frame = single, breaklines = true]
    cd ~/ENVISIoN/scripts
    ./install.sh /home/$USER/ENVISIoN /home/$USER/inviwo
\end{lstlisting}

Once the installation script has run, it prints build instructions.
Follow the instructions and start the build. The instructions will
tell you to \emph{cd} to the build directory and execute make.

An easy way to modify the build settings, if needed, is to install
the cmake curses gui and run it in the build directory.

To install the cmake gui:
\begin{lstlisting}[frame = single, breaklines = true]
    sudo apt install cmake-curses-gui
\end{lstlisting}

Running cmake in the build directory:
\begin{lstlisting}[frame = single, breaklines = true]
    cd ~/inviwo/build
    ccmake .
\end{lstlisting}

When in the GUI, press \emph{c} to apply the current configuration,
\emph{g} to generate build files and \emph{q} to quit. If settings
have changed, it is possible that you will need to press \emph{c} more
than once before the \emph{g} option becomes available.

After having generated the build files, the project can now be rebuilt
with the new settings by executing \emph{make} like earlier.