\section{Licens}
\label{ref:licens}
Copyright (c) 2017: Josef Adamsson, Robert Cranston, David Hartman, Denise Härnström, Fredrik Segerhammar. \textit{(Teknisk dokumentation - release 1)}\newline
Copyright (c) 2018: Anders Rehult, Andreas Kempe, Marian Brännvall, Viktor Bernholtz. \textit{(Teknisk dokumentation - release 2)}\newline
Copyright (c) 2019: Linda Le, Abdullatif Ismail, Anton Hjert, Lloyd Kizito and Jesper Ericsson. \textit{(Teknisk dokumentation - release 3)}\newline
Copyright (c) 2017: 2019 - Rickard Armiento, Johan Jönsson

All rights reserved.

Redistribution and use in source and binary forms, with or without
modification, are permitted provided that the following conditions are met:

1. Redistributions of source code must retain the above copyright notice, this list of conditions and the following disclaimer.\newline
2. Redistributions in binary form must reproduce the above copyright notice, this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.

THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS AS IS AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING,
BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING
NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
