\addcontentsline{toc}{section}{Referenser}
\begin{thebibliography}{99}

\bibitem{API} \textit{API -} URL: \textit{https://www.ne.se/uppslagsverk/encyklopedi/lång/api-(data)} \\ (hämtad 2019-05-16)

\bibitem{BSD2} \textit{BSD2 -} URL: \textit{https://opensource.org/licenses/BSD-2-Clause} \\
(hämtad 2019-05-10)

\bibitem{C++} \textit{C++} URL: \textit{http://www.cplusplus.com/info/description/} (hämtad 2019-01-28).

\bibitem{dict} \textit{Data Structures} URL: \textit{https://docs.python.org/3/tutorial/datastructures.html} (hämtad 2019-05-17).

\bibitem{Fermi-energi} \textit{Solid State Physics -} Neil Ashcroft och David Mermin, 1976, s. 141.

\bibitem{Git} \textit{Git} URL: \textit{https://git-scm.com} (hämtad 2019-01-28).

\bibitem{GUI} \textit{GUI -} URL: \textit{https://www.ne.se/uppslagsverk/encyklopedi/lång/api-(data)}
\\(hämtad 2019-05-10)

\bibitem{High Level Introduction to HDF5} \textit{High Level Introduction to HDF5} URL: \textit{https://support.hdfgroup.org/HDF5/Tutor/HDF5Intro.pdf} (hämtad 2019-02-27).

\bibitem{How To Use HDF5 Files in Python} \textit{How To Use HDF5 Files in Python} URL: \textit{https://www.pythonforthelab.com/blog/how-to-use-hdf5-files-in-python/} (hämtad 2019-02-26).

\bibitem{Inviwo} \textit{Inviwo -} URL: \textit{https://inviwo.org/} (hämtad 2019-05-10)

\bibitem{Python} \textit{Python} URL: \textit{https://www.python.org/} (hämtad 2019-01-28)

\bibitem{Python3} \textit{Python3 -} URL: \textit{https://docs.python.org/3/} (hämtad 2019-05-10)

\bibitem{PyQT} \textit{PyQT -} URL:
\textit{https://www.riverbankcomputing.com/static/Docs/PyQt5/} (hämtad 2019-05-16)

\bibitem{what is array} \textit{Python Arrays} URL: \textit{https://www.programiz.com/python-programming/array\#introduction} (hämtad 2019-05-21).

\bibitem{what is UNIX} \textit{What is UNIX?} URL: \textit{https://www.softwaretestinghelp.com/unix-introduction/} (hämtad 2019-05-21).

\bibitem{wxPython} \textit{wxPython -} URL:
\textit{https://wxpython.org/pages/overview/} (hämtad 2019-05-16)

\bibitem{wxPythonDoc} \textit{wxPython Documentation} URL: \textit{https://docs.wxpython.org/wx.1moduleindex.html} (hämtad 2019-05-17)

\bibitem{Quick Start Guide} \textit{Quick Start Guide} URL: \textit{http://docs.h5py.org/en/stable/quick.html\#appendix-creating-a-file} (hämtad 2019-02-26).

\bibitem{Radial distribution function}
\textit{Radial distribution function} URL: \textit{https://en.wikipedia.org/wiki/Radial\_distribution\_function}
(hämtad 2019-03-03).

\bibitem{HDF group} \textit{The HDF Group, Hierarchical Data Format, version 5 1997-2019} \\
URL: \textit{https://support.hdfgroup.org/HDF5/} 
(hämtad 2018-01-28).

\bibitem{HDF group2}
\textit{The HDF Group. High Level Introduction to HDF5. 23 sept. 2016} \\ URL: \textit{https://support.hdfgroup.org/HDF5/Tutor/HDF5Intro.pdf} (hämtad 2019-01-28).

\bibitem{Unittest} \textit{Unittest} URL: \textit{https://docs.python.org/3/library/unittest.html} (hämtad 2019-03-06).

\bibitem{VASP} \textit{VASP} URL: \textit{https://www.vasp.at/index.php/about-vasp/59-about-vasp} (hämtad 2019-02-26).




 
\end{thebibliography}